---
title: "Assignment2"
output:
  pdf_document: default
date: "2022-09-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

--
title: "Assignment2"
output: pdf_document
---


```{r}
setwd("C:/Users/haris/Documents/Fall 2022/Quantitative Management Modelling/Assignment 2")
```

#Further down, we need to specify the objective, constraints, direction, and constants in order to solve the problem.

__Objective Function__

__The Objective function is to Max Z = 420(L1 + L2 + L3) + 360(M1 + M2 + M3) + 300(S1 + S2 + S3)__


__It can be written as Z = 420L1 + 360M1 + 300S1 + 420L2 + 360M2 + 300S2 + 420L3 + 360M3 + 300S3__


        L1 + M1 + S1 <= 750
        
        L2 + M2 + S2 <= 900
        
        L3 + M3 + S3 <= 450
        
        20L1 + 15M1 + 12S1 <= 13000
        
        20L2 + 15M2 + 12S2 <= 12000
        
        20L3 + 15M3 + 12S3 <= 5000
        
        L1 + L2 + L3 <= 900
        
        M1 + M2 + M3 <= 1200
        
        S1 + S2 + S3 <= 750
        
__Non Negativity Constraints__

        L1, L2, L3, M1, M2, M3, S1, S2, S3 >= 0
      

__The above constraints can be written as below__

        L1 + M1 + S1 + 0*L2 + 0*M2 + 0*S2 + 0*L3 + 0*M3 + 0*S3 <= 750

        0L1 + 0M1 + 0S1 + L2 + M2 + S2 + 0L3 + 0M3 + 0S3 <= 900

        0L1 + 0M1 + 0S1 + 0L2 + 0M2 + 0S2 + L3 + M3 + S3 <= 450

        20L1 + 15M1 + 12S1 + 0L2 + 0M2 + 0S2 + 0L3 + 0M3 + 0S3 <= 13000

        0L1 + 0M1 + 0S1 + 20L2 + 15M2 + 12S2 + 0L3 + 0M3 + 0S3 <= 12000

        0L1 + 0M1 + 0S1 + 0L2 + 0M2 + 0S2 + 20L3 + 15M3 + 12S3 <= 5000

        L1 + 0M1 + 0S1 + L2 + 0M2 + 0S2 + L3 + 0M3 + 0S3 <= 900

        0L1 + M1 + 0S1 + 0L2 + M2 + 0S2 + 0L3 + M3 + 0S3 <= 1200

        0L1 + 0M1 + S1 + 0L2 + 0M2 + S2 + 0L3 + 0M3 + S3 <= 750



```{r}
library("lpSolve")
#Defining the Objective Function - f.obj

f.obj <- c(420,360,300,420,360,300,420,360,300)

#Defining the Constraints - f.con

f.con <- matrix(c(1,1,1,0,0,0,0,0,0,
0,0,0,1,1,1,0,0,0,
0,0,0,0,0,0,1,1,1,
20,15,12,0,0,0,0,0,0,
0,0,0,20,15,12,0,0,0,
0,0,0,0,0,0,20,15,12,
1,0,0,1,0,0,1,0,0,
0,1,0,0,1,0,0,1,0,
0,0,1,0,0,1,0,0,1), nrow = 9, byrow=T)

#Defining the Direction of the constraints - f.dir

f.dir <- c('<=',
           
          '<=',
           
          '<=',
           
          '<=',
           
          '<=',
           
          '<=',
           
          '<=',
           
          '<=',
           
          '<=')


#Defining the constants i.e. the right hand side values - f.rhs

f.rhs <- c(750,900,450,13000,12000,5000,900,1200,750)

#Calling the lp function to solve the problem basing the objective function i.e. to maximize the profits

lp('max',f.obj,f.con,f.dir,f.rhs)


#Calling the lp function again to get the values for the variables defined above

lp('max',f.obj,f.con,f.dir,f.rhs)$solution


```







