---
title: "Assignment 3"
author: "Harish Kumar uddandi"
date: "10/18/2022"
output: pdf_document
---

1) Formulating Transportation using R
```{r}
library(lpSolveAPI)
library(tinytex)
library(lpSolve)

```

# This data has to be transformed into a table format.
```{r}
#cost matrix
cost_1 <- matrix(c(22,14,30,600,100,
                 16,20,24,625,120,
                 80,60,70,"-","-","210/220"),ncol = 5,nrow = 3,byrow = TRUE)
colnames(cost_1) <- c("Warehouse_1", "Warehouse_2","Warehouse_3","ProductionCost","Production Capacity")

rownames(cost_1) <- c("Plant_A","Plant_B","Demand")

cost_1
```
The Objective function is to Minimize the TC
$$  \text{Min} \hspace{.2cm} TC = 622 x_{11} + 614 x_{12} + 630 x_{13} + 641 x_{21} + 645 x_{22} + 649 x_{23}$$
Supply
$$X_{11} + X_{12} + X_{13}  >= 100$$
$$X_{21} + X_{22} + X_{23} >= 120$$
   
   
Demand
$$ X_{11} + X_{21} >= 80$$
$$ X_{12} + X_{22} >= 60$$
$$ X_{13} + X_{23} >= 70$$


Non-Negativity Constraints
$$ X_{ij} >= 0$$ 
Where i = 1,2 and j= 1,2,3
 
```{r}

#A "Dummy" row for Warehouse_4 Is added here
trans.cost_1 <- matrix(c(622,614,630,0,100,
                       641,645,649,0,120,
                       80,60,70,10,220), ncol = 5, nrow = 3, byrow = TRUE)
trans.cost_1
```

```{r}

colnames(trans.cost_1) <- c("Warehouse_1","Warehouse_2","Warehouse_3","Dummy","Production Capacity")

rownames(trans.cost_1) <- c("Plant_1", "Plant_2","Monthly Demand")
trans.cost_1
```
 
```{r}
#costs matrix
costs <- matrix(c(622,614,630,0,
                  641,645,649,0), nrow = 2, byrow = TRUE)
costs

```

It is important to understand that the Supply function cannot be greater than the stated units, although the Demand function can.


```{r}
#setting up constraint signs and right-hand sides(supply side)
row.signs <- rep("<=",2)
row.rhs <- c(100,120)

#Demand constraints#
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)

```

```{r}

lptrans <- lp.transport(costs, "min", row.signs,row.rhs,col.signs,col.rhs)

```

```{r}
lptrans$solution
```
80 AEDs in Plant 2 - Warehouse_1

60 AEDs in Plant 1 - Warehouse_2

40 AEDs in Plant 1 - Warehouse_3

30 AEDs in Plant 2 - Warehouse_3


```{r}
lptrans$objval
```
The combined cost of production and shipping for the defibrilators is $132,790
```{r}
lptrans$duals
```


2)Formulate the dual of the transportation problem

Since the primal was to minimize the transportation cost the dual of it would be to maximize the value added(VA). 

```{r}
cost_2 <- matrix(c(622,614,630,100,"u1",
                   641,645,649,120,"u2",
                   80,60,70,220,"-",
                   "v1","v2","v3","-","-"),ncol = 5,nrow = 4,byrow = TRUE)
colnames(cost_2) <- c("Warehouse_1", "Warehouse_2","Warehouse_3","Production Capacity","Supply(Dual)")

rownames(cost_2) <- c("Plant_A","Plant_B","Demand","Demand(Dual)")
```




$$  \text{Max} \hspace{.2cm} VA = 100 P_{1} + 120 P_{2} +80 W_{1} + 60 W_{2} + 70 W_{3}$$


Subject to the following constraints
Total Profit Constraints
$$ u_{1} + v_{1} <= 622$$
$$ u_{1} + v_{2} <= 614$$
$$ u_{1} + v_{3} <= 630$$
$$ u_{2} + v_{1} <= 641$$
$$ u_{2} + v_{2} <= 645$$
$$ u_{2} + v_{3} <= 649$$
These are taken from the transposed matrix of the Primal of the LP. These are unrestricted where $$ u_{k} , v_{l}$$ where u=1,2 and v=1,2,3

```{r}
#Objective function

f.obj <- c(100,120,80,60,70)

#transposed from the constraints matrix in the primal
f.con <- matrix(c(1,0,1,0,0,
                  1,0,0,1,0,
                  1,0,0,0,1,
                  0,1,1,0,0,
                  0,1,0,1,0,
                  0,1,0,0,1), nrow = 6, byrow = TRUE)

f.dir <- c("<=",
           "<=",
           "<=",
           "<=",
           "<=",
           "<=")

f.rhs <- c(622,614,630,641,645,649)
lp("max",f.obj,f.con,f.dir,f.rhs)

lp("max",f.obj,f.con,f.dir,f.rhs)$solution
```
Z=139,120 and variables are:
$$ u_{1} = 614$$
$$ u_{2} = 633$$ 
$$ v_{1} = 8$$
$$ v_{3} = 16$$
So Z = $139,120 and variables are $$ u_{1} = 614$$ which represents Plant A
$$u_{2}=633$$    which stands for  Plant B
$$v_{1}=8$$      which stands for  Warehouse_1
$$v_{2}=16$$     which stands for  Warehouse_3


3) Economic Interpretation of the dual

  minimal Z(Primal) = 132790 
  maximum Z(Dual) =  139120. 
 We came to the conclusion that we shouldn't be shipping from  Plants (A/B) to all three Warehouses. Where we ought to be shipping from:

$$ 60 X_{12}$$ which is 60 Units from Plant A to Warehouse 2.
$$ 40 X_{13}$$ which is 40 Units from Plant A to Warehouse 3.
$$ 80 X_{13}$$ which is 60 Units from Plant B to Warehouse 1.
$$ 30 X_{13}$$ which is 60 Units from Plant B to Warehouse 3.

We will Max the profit from each distribution to the respective capacity.

From the above using  the Sensitivity and Duality, the shadow price can be tested.
Change 100 to 101 and 120 to 121 in our LP Transport.

```{r}
row.rhs1 <- c(101,120)
row.signs1 <- rep("<=",2)
col.rhs1 <- c(80,60,70,10)
col.signs1 <- rep(">=",4)
row.rhs2 <- c(100,121)
row.signs2 <- rep("<=",2)
col.rhs2 <- c(80,60,70,10)
col.signs2 <- rep(">=",4)

lp.transport(costs,"min",row.signs,row.rhs,col.signs,col.rhs)

lp.transport(costs,"min",row.signs1,row.rhs1,col.signs1,col.rhs1)

lp.transport(costs,"min",row.signs2,row.rhs2,col.signs2,col.rhs2)

```

The 'min' of the specific function is taken here and we observe that the number goes down by 19. 
This indicates the shadow price is 19.

From the dual variable $$ v_{1}$$ where Marginal Revenue <= Marginal Cost. The equation was $$ \hspace{2cm} u_{2}\le 645 - v_{2} => 633\le645 - 0 = 645=> Incorrect$$ and this was found by using $$ \hspace{2cm} u_{1} ^0 -v_{1} ^0 \le 622 $$ then we subtract $$ \hspace{2cm} v_{1} ^0 $$ to the other side to get  $$\hspace{2cm} u_{1} ^0\le 622 - v_{1} ^0 $$

The economic interpretation of the dual follows the universal rule of profit maximization which is MR >= MC 

```{r}
lp("max", f.obj,f.con, f.dir,f.rhs)$solution
```

Warehouse1 >= Plant1 + 621 i.e. MR1 >= MC1

$$ 60 X_{12}$$ which is 60 Units from Plant A to Warehouse 2.
$$ 40 X_{13}$$ which is 40 Units from Plant A to Warehouse 3.
$$ 80 X_{13}$$ which is 60 Units from Plant B to Warehouse 1.
$$ 30 X_{13}$$ which is 60 Units from Plant B to Warehouse 3.


The condition is not satisfied by Plant B to Warehouse 2. As a result, no AED device will be shipped.

